---
title: "Final Project Presentation"
author: "Xiang Zhao"
date: "12/18/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(streamR)
library(stringr)
library(wordcloud)
library(tm)
library(dplyr)
library(leaflet)
library(lubridate)
library(wordcloud)
library(ggplot2)
library(plotly)
library(maps)
library(maptools)
```
# Content
## Content
Introduction

Cybersecutiry: Word Cloud, Timeline & Map

Cyberthreats: Word Cloud

Protection Software: Word Cloud & Sentiment Analysis

# Introduction
## Introduction
2017 Cyberthreats Defense Report have done a survey and data analysis on successful cyberattacks a company or an organization experienced in 15 countries. 

It shows that 80.6% respondents in America have compromised by at least one successful cyberattack in the past 12 months. The beast situation happened in Brazil and the worst situation happpened in China, 64.7% and 95.9%.

## Introduction
It's not hard to see the severity of cyberattack and importance of cybersecurity. 

Thus, I choose cybersecurity and cyberattack(cybercrime) as my topics to see the reactions and comments people have on social media Twitter.

I will use text analysis and mapping to see the where and what kind of reactions and comments peopel have gloabally. And also I select first two best protection softwares against cyberattacks, using sentiment analysis to see people's attitude towards these two softwares.

# Cybersecurity

## Cybersecurity
Word Cloud
```{r,message=FALSE,warning=FALSE}
cybersecurity.df <- readRDS("cybersecurity.df.rds")
cyberword <- Corpus(VectorSource(str_replace_all(cybersecurity.df$text, "@", "")))
cyberword <- tm_map(cyberword, removePunctuation)
cyberword <- tm_map(cyberword, content_transformer(tolower))
cyberword <- tm_map(cyberword, removeWords, stopwords("english"))
cyberword <- tm_map(cyberword, removeWords, c("cybersecurity","cyber","security","levelnet","amp","visit","part"))
cyberword <- tm_map(cyberword, stripWhitespace)

pal <- brewer.pal(9,"Blues")
pal <- pal[-(1:4)]
set.seed(123)
wordcloud(words = cyberword, scale=c(2.5,0.2), max.words=300, random.order=FALSE, 
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(9,"Blues")[5:9])
```

Key words: "entrepreneurial", "timmaliyil" and "blockchain"

## Cybersecurity
Timeline
```{r,message=FALSE,warning=FALSE}
#Timeline
cybersecurity.df$favoriteCount <- as.numeric(cybersecurity.df$favoriteCount)
t1 <- ggplot(cybersecurity.df, aes(x = created))
t1 <- t1 + geom_line(aes(y = favoriteCount),color = "navy")
t1 <- t1 + labs(x="Time", y="Number of Favorites")
ggplotly(t1)
```

## Cybersecurity
Map
```{r,message=FALSE,warning=FALSE}
#Mapping
cybersecurity.geo <- readRDS("cybersecurity.geo.rds")
cybersecurity.geo$longitude <- as.numeric(cybersecurity.geo$longitude)
cybersecurity.geo$latitude <- as.numeric(cybersecurity.geo$latitude)
map <- NULL
mapworld <- borders("world", colour="gray45", fill="light green") # create a layer of borders
map <- ggplot() +   mapworld
map <- map+ geom_point(aes(longitude,latitude), data = cybersecurity.geo, color="dark red", size=2.5) 
map <- map + theme_bw()
ggplotly(map)
```

The USA and India.

## Cybercrime
Word Cloud
```{r,message=FALSE,warning=FALSE}
cybercrime.df <- readRDS("cybercrime.df.rds")
crimeword <- Corpus(VectorSource(str_replace_all(cybercrime.df$text, "@", "")))
crimeword <- tm_map(crimeword, removePunctuation)
crimeword <- tm_map(crimeword, content_transformer(tolower))
crimeword <- tm_map(crimeword, removeWords, stopwords("english"))
crimeword <- tm_map(crimeword, removeWords, c("cybercrime","cyber","crime","cybersecurity","security","amp"))
crimeword <- tm_map(crimeword, stripWhitespace)

pal <- brewer.pal(9,"Reds")
pal <- pal[-(1:4)]
set.seed(168)
wordcloud(words = crimeword, scale=c(2.5,0.2), max.words=300, random.order=FALSE, 
          rot.per=0.35, use.r.layout=T, colors=brewer.pal(9,"Reds")[5:9])
```

Key words: "infosec", "bitcoin", "banking","hacking","frauds","big data" and "machine learning"

## Cyberattack
Word Cloud
```{r,message=FALSE,warning=FALSE}
cyberattack.df <- readRDS("cyberattack.df.rds")
attackword <- Corpus(VectorSource(str_replace_all(cyberattack.df$text, "@", "")))
attackword <- tm_map(attackword, removePunctuation)
attackword <- tm_map(attackword, content_transformer(tolower))
attackword <- tm_map(attackword, removeWords, stopwords("english"))
attackword <- tm_map(attackword, removeWords, c("cyber","cyberattack","attack","cybersecurity"))
attackword <- tm_map(attackword, stripWhitespace)


set.seed(168)
wordcloud(words = attackword, scale=c(3,0.2), max.words=300, random.order=FALSE, 
          rot.per=0.35, use.r.layout=T, colors=brewer.pal(9,"Reds")[5:9])
```

Key words:  "data", "hackers", "business" and "infosec" 

## Bitdefender
Word Cloud
```{r,message=FALSE,warning=FALSE}
bitdefender.df <- readRDS("bitdefender.df.rds")
bitword <- Corpus(VectorSource(str_replace_all(bitdefender.df$text, "@", "")))
bitword <- tm_map(bitword, removePunctuation)
bitword <- tm_map(bitword, content_transformer(tolower))
bitword <- tm_map(bitword, removeWords, stopwords("english"))
bitword <- tm_map(bitword, removeWords, c("cybercrime","cyber","crime","cybersecurity","security","software","securitysoftware","bitdefender"))
bitword <- tm_map(bitword, stripWhitespace)

set.seed(168)
wordcloud(words = bitword, scale=c(3,0.2), max.words=300, random.order=FALSE, 
          rot.per=0.35, use.r.layout=T, colors=brewer.pal(9,"Greens")[5:9])
```

Key words: "antivirus", "android", "microsoft" and "million"

## Kaspersky
Word Cloud
```{r,message=FALSE,warning=FALSE}
kaspersky.df <- readRDS("kaspersky.df.rds")
kpword <- Corpus(VectorSource(str_replace_all(kaspersky.df$text, "@", "")))
kpword <- tm_map(kpword, removePunctuation)
kpword <- tm_map(kpword, content_transformer(tolower))
kpword <- tm_map(kpword, removeWords, stopwords("english"))
kpword <- tm_map(kpword, removeWords, c("cybercrime","cyber","crime","cybersecurity","security","software","securitysoftware","bitdefender","kaspersky"))
kpword <- tm_map(kpword, stripWhitespace)

pal <- brewer.pal(9,"Greens")
pal <- pal[-(1:4)]
set.seed(168)
wordcloud(words = kpword, scale=c(3,0.2), max.words=300, random.order=FALSE, 
          rot.per=0.35, use.r.layout=T, colors=brewer.pal(9,"Greens")[5:9])
```

Key words: "federal" and "government"

```{r,message=FALSE,warning=FALSE}
#Sentiment Analysis
bitdefender.df <- readRDS("bitdefender.df.rds")
kaspersky.df <- readRDS("kaspersky.df.rds")
pos.words <- scan("positive-words.txt",what="character",comment.char=";")
neg.words <- scan("negative-words.txt",what="character",comment.char=";")

pos.words = c(pos.words, 'new','nice' ,'good')
neg.words = c(neg.words, 'wtf', 'ugly','worse', 'shitty', 'bad', 'no', 'freaking','sucks', 'horrible')

score.sentiment = function(sentences, pos.words, neg.words, .progress='none')
{
	require(plyr)
	require(stringr)
	
	# we got a vector of sentences. plyr will handle a list or a vector as an "l" for us
	# we want a simple array of scores back, so we use "l" + "a" + "ply" = laply:
	scores = laply(sentences, function(sentence, pos.words, neg.words) {
		
		# clean up sentences with R's regex-driven global substitute, gsub():
		sentence = gsub('[[:punct:]]', '', sentence)
		sentence = gsub('[[:cntrl:]]', '', sentence)
		sentence = gsub('\\d+', '', sentence)
		# and convert to lower case:
		sentence = tolower(sentence)

		# split into words. str_split is in the stringr package
		word.list = str_split(sentence, '\\s+')
		# sometimes a list() is one level of hierarchy too much
		words = unlist(word.list)

		# compare our words to the dictionaries of positive & negative terms
		pos.matches = match(words, pos.words)
		neg.matches = match(words, neg.words)
	
		# match() returns the position of the matched term or NA
		# we just want a TRUE/FALSE:
		pos.matches = !is.na(pos.matches)
		neg.matches = !is.na(neg.matches)

		# and conveniently enough, TRUE/FALSE will be treated as 1/0 by sum():
		score = sum(pos.matches) - sum(neg.matches)

		return(score)
	}, pos.words, neg.words, .progress=.progress )

	scores.df = data.frame(score=scores, text=sentences)
	return(scores.df)
}

bitdefender.df$text <- str_replace_all(bitdefender.df$text, "@", "")
kaspersky.df$text <- str_replace_all(kaspersky.df$text, "@", "")
bit_result <- score.sentiment(bitdefender.df$text,pos.words,neg.words)
saveRDS(bit_result,"bit_result.rds")
write.csv(bit_result,"bit_result.csv")
kp_result <- score.sentiment(kaspersky.df$text,pos.words,neg.words)
saveRDS(kp_result,"kp_result.rds")
```

## Bitdefender & Kaspersky
Sentiment Analysis
```{r,message=FALSE,warning=FALSE}
#Plot of score
#bit_result <- read.csv("bit_result.csv")
#bit_result <- readRDS("bit_result.rds")
#kp_result <- readRDS("kp_result.rds")
sent1 <- ggplot(data=bit_result, aes(bit_result$score)) + geom_histogram(fill = "yellow", binwidth = 0.5) + theme_bw() + scale_x_continuous(breaks=seq(-4, 4, 1)) + geom_vline(xintercept = mean(bit_result$score),color = "red",size = 1.3) + labs(title = "Histogram of sentiment score of Bitdefender", y = "Frequency", x= "Score")
ggplotly(sent1)
```

## Bitdefender & Kaspersky
Sentiment Analysis
```{r,message=FALSE,warning=FALSE}
sent2 <- ggplot(data=kp_result, aes(kp_result$score)) + geom_histogram(fill = "yellow", binwidth = 0.5) + theme_bw() + scale_x_continuous(breaks=seq(-4, 5, 1)) + geom_vline(xintercept = mean(kp_result$score),color = "red",size = 1.3) + labs(title = "Histogram of sentiment score of Kaspersky", y = "Frequency", x= "Score")
ggplotly(sent2)
```

## Bitdefender & Kaspersky
Sentiment Analysis

From histogram of sentiment score of Bitdefender, we see that the range is from -4 to 4, and a vast majority of sentences have 0 score which means most of them are neutral. The red line indicates the mean of score which is -0.22, so it's knid of lightly negative attitude of people towards Bitdefender.

From histogram of sentiment score of Kaspersky, we see that the range is from -4 to 5 which means a wider positive range than Bitdefender, and a vast majority of sentences have 0 or 1 score. The red line indicates the mean of score which is 0.27, so it's knid of lightly positive attitude of people towards Kaspersky. Thus, comparing Bitdefender and Kaspersky from tweets, we can conclude that Kaspersky has a relatively positive reputation than Bitdefender.

# Thanks!


